The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-12-20 paper/main.tex
update paper text and figures

\title{ The effects of binarity on planet occurrence rates measured by transit 
surveys}
%
\correspondingauthor{L. Bouma}
\email{luke@astro.princeton.edu}
%
\author{L. G. Bouma}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{K. Masuda}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{J. N. Winn}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
%
%
\begin{abstract}
%
This study develops simplified models of signal-to-noise limited transit 
surveys, in order to clarify the biases that stellar binarity introduces
to occurrence rate measurements.
Particular attention is paid to dilution of observed planet radii, errors in 
star counts, and detection efficiencies.
Free parameters in our models include the true radius distribution of planets, 
and the relative numbers of planets orbiting secondaries, primaries, and 
single stars.
In the simplest possible case, all stellar systems are either single or twin 
binaries, and all planets are identical. If so, then we find that ignoring 
binarity leads to an underestimate of the occurrence at the true radius by a 
multiplicative factor of $0.76$ (assuming a 10\% twin binary fraction).
Using more realistic models for the stellar population and planetary 
radii, we find that the occurrence of Earth-sized planets can be overestimated 
by at most $\approx 50\%$ when ignoring binarity~--~at present far smaller 
than systematic uncertainties on real $\eta_\oplus$ measurements.
We quantify how gaps in the intrinsic planet radius distribution are filled 
in when binarity is neglected.
Our models suggest that for most of the observed radius distribution 
($r>2r_\oplus$), ignoring binarity only leads to errors in inferred occurrence 
rates at the $\lesssim 10\%$ level.
One corollary is that binarity is unlikely to strongly influence the HJ rate 
discrepancy.
%
\end{abstract}
%
\keywords{
    methods: data analysis ---
    planets and satellites: detection ---
    surveys}
%
%

@@

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        Inferred occurrence rates over $0.01r_\oplus$ bins in planet 
        radius, for a model with identical stars, identical planets, and twin 
        binaries.
        We assume a twin binary fraction of ${\rm BF}=0.1$, and that all 
        stars (single, primary, and secondary) host planets at equal 
        rates.
        If the true planet radius is $r\p$, all planets detected in binaries 
        will have apparent radii $r\a = r\p/\sqrt{2}$.
    }
    \label{fig:occ_rate_model_1}
\end{figure}

@@

To generalize the procedure of Sec.~\ref{sec:simplest}, we consider a S/N 
limited transit survey in which all the primaries and single stars have 
identical properties.
For example, they might all be solar analogs, roughly similar to 
the stars that {\it Kepler} surveyed~\citep{batalha_selection_2010}.
We let the properties of the secondaries vary, and assume that there are some 
functions $L(M)$ and $R(M)$ that specify a star's luminosity and radius in 
terms of its mass.
We then allow for an arbitrary volume-limited mass ratio distribution 
$f(q)$, and also for arbitrary true rate densities for singles, primaries, 
and doubles ($\Gamma_0, \Gamma_1, \Gamma_2$).
Since the properties of the secondaries vary, we must consider not only the 
dependence of the rate densities on planet radius, but also on stellar mass.
We presume that the observers always take the properties of a binary system to 
be those of the primary.

@@

\begin{figure}[!tb]
    \centering
    \epsscale{1.15}
    \plottwo{figures/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf}
    \caption{
        {\it Left:} rate density and {\it right:} rate (over $0.5r_\oplus$ 
        bins) as a function of planet radius for the distribution specified by 
        Eq.~\ref{eq:model3_radius_distribution}. This model has identical 
        primaries and single stars, and varying secondaries. We use an 
        arbitrary normalization of $Z_0=0.5$ throughout.}
    \label{fig:occ_rate_model_3_log}
\end{figure}

@@

@@

\begin{figure}[!tb]
    \centering
    \epsscale{1.15}
    \plottwo{figures/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf}
    \caption{
        {\it Left:} rate density and {\it right:} rate (over $0.25r_\oplus$ 
        bins) as a function of planet radius in a model with a radius gap 
        (Eq.~\ref{eq:model4_radius_distribution}).
        Similar to Fig.~\protect\ref{fig:occ_rate_model_3_log}, this model has 
        fixed primaries and single stars, but varying secondaries.
    }
    \label{fig:model_4}
\end{figure}

@@

@@

\paragraph{How has binarity been considered in occurrence rate measurements?}
This study has shown that under a reasonable set of simplifying assumptions, 
binarity can introduce systematic errors to star and planet counts in transit 
surveys, which then bias derived occurrence rates.
Thus far, real-world occurrence rate calculations\footnote{
    A list of occurrence rate papers is maintained at 
    \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
} using transit survey data have mostly ignored stellar 
multiplicity~\citep[\textit{e.g.},][]{howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,dressing_occurrence_2015,burke_terrestrial_2015}.
For {\it Kepler} occurrence rates specifically, 
it seems that no one has yet carefully assessed binarity's importance, or lack 
thereof.
While we do not resolve the problem, we do suggest the approximate scale of 
the necessary corrections in a survey-independent manner.

Of course, on a system-by-system level stellar multiplicity affects the 
interpretation of planet candidates. High resolution imaging 
campaigns have measured the multiplicity of almost all {\it Kepler}\ Objects 
of Interest 
\citep{howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
    horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
    law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
    wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016,ziegler_robo-ao_2017}.
The results of these programs have been collected 
by~\citet{furlan_kepler_2017}, and they represent an important advance in 
understanding the KOI 
sample's multiplicity statistics.
In particular, they can be immediately applied to rectify binarity's effects 
on the mass-radius diagram~\citep{furlan_densities_2017}.

The high resolution imaging campaign is also beginning to connect with
occurrence rate calculations.
The most recent rate studies have used~\citet{furlan_kepler_2017}'s 
catalog to test the effects of removing KOI hosts with known companions, which 
helps reduce contamination in the ``numerator'' of 
the occurrence rate (\citealt{fulton_california-_2017}; 
\citealt{petigura_CKS_2017}).
However, without an understanding of the multiplicity statistics of the 
non-KOI stars, the true number of searchable stars, and thus the true 
occurrence rates, will remain biased.
The first-order correction that we suggest, given the impracticality of 
performing high-resolution imaging of every star searched by a transit 
survey, is to model the detection pipeline's efficiency while accounting for 
binarity.
For {\it Kepler}, this would require high resolution imaging of a
comparison sample of non-KOI host stars. If the associated multiplicity 
statistics are then included in a model of the pipeline's detection 
efficiency, and the number of searchable stars is appropriately counted (at a 
given $\delta_{\rm obs}$), it would correct many of binarity's biases.

\paragraph{The rate of Earth analogs}
Per {\it Kepler}'s primary science objective, the rate of Earth-like planets 
orbiting Sun-like stars has been independently measured by 
\citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
    foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
These efforts have found that the one-year terrestrial planet occurrence rate 
varies between $\approx 0.03$ and $\approx 1$ per Sun-like star, depending on 
assumptions that are made when retrieving the rate 
(\citealt{burke_terrestrial_2015}'s Fig.~17).
In the power law model of Sec.~\ref{sec:model_3}, the inferred rate can be up 
to 50\% higher than the true rate around single stars.
Though this bias seems large, it is currently small compared to the other 
systematic factors that dominate the dispersion in $\eta_\oplus$ 
measurements.
If a future analyses determine absolute values of $\eta_\oplus$ to 
better than a factor of two, binarity might merit closer attention.

One relevant caveat to our assessment of binarity's importance for 
$\eta_\oplus$ measurements is that none of our models 
included the rate density's period-dependence. However, close binaries usually
provoke dynamical instabilities, leading to fewer long-period planets per 
star~\citep[\textit{e.g.},][]{holman_long-term_1999,wang_influence_2014,
    kraus_impact_2016}.
This effect might further bias transit survey measurements of $\eta_\oplus$
beyond our rough estimate.

\paragraph{The hot Jupiter rate discrepancy}
There is at least one context in which ignoring binarity has been suggested as 
a possible source of discrepant occurrence rate measurements.
Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
marginally lower than those found by radial velocity surveys ($\approx 1\%$; 
see Table~\ref{tab:hj_rates}).
Though the discrepancy has weak statistical significance ($<3\sigma$),
one reason to expect a difference is that the corresponding stellar 
populations have distinct metallicities.
As argued by \citet{gould_frequency_2006}, the RV sample is biased towards 
metal-rich stars, which have been measured by RV surveys to preferentially 
host more giant 
planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005}.
Investigating the discrepancy from the metallicty 
angle,~\citet{guo_metallicity_2017} measured the
{\it Kepler} field's mean metallicity to be $[{\rm M/H}]_{\rm Kepler}= 
-0.045\pm0.009$, which is lower than the California Planet Search's mean of 
$[{\rm M/H}]_{\rm CPS}= -0.005\pm0.006$.
The former value agrees with that measured by \citet{dong_metallicities_2014}.
Refitting for the metallicity exponent in $\Lambda_{\rm HJ} \propto 10^{\beta 
[{\rm M/H}] }$, \citeauthor{guo_metallicity_2017}\! found $\beta = 2.1\pm 
0.7$, and noted that this would imply that the metallicity difference could 
account for a $\approx 20\%$ relative difference in the measured rates between 
the CKS and {\it Kepler}\ samples~--~not a factor of two\footnote{
\citet{petigura_CKS_2017} recently found $\beta = 3.4^{0.9}_{-0.8}$.
This gives an $\approx 25\%$ relative difference, indicating metallicity could 
account for at least half of the ``hot Jupiter rate discrepancy''.
}.
\citeauthor{guo_metallicity_2017}\! concluded that ``other factors, such as 
binary contamination and imperfect stellar properties'' must also be at play.

@@

\paragraph{Does a detected planet orbit the primary or secondary?}
\citet{ciardi_understanding_2015} studied the effects of stellar multiplicity 
on the planet radii derived from transit surveys.
They modeled the problem for {\it Kepler}\ objects of interest by matching a 
population of binary and tertiary companions to KOI stars, 
under the assumption that the KIC-listed stars were the primaries.
They then computed planet radius correction factors assuming that {\it 
    Kepler}-detected planets orbited the primary or companion stars
with equal probability (their Sec.~5).
Under these assumptions, they found that any given planet's radius is on 
average underestimated by a multiplicative factor of $\approx\! 1.5$.
\citet{ziegler_robo-ao_2017} recently reported a similar value for the real
population of systems observed by the Robo-AO KOI survey, under the same 
assumption.

Our models indicate that assuming a detected planet has equal probability of 
orbiting the primary or secondary leads to an overestimate of
binarity's population-level effects.
A planet orbiting the secondary does lead to extreme corrections, but these 
cases are rare outliers, because the searchable volume for secondaries is so 
much smaller than that for primaries (see~Fig.~\ref{fig:model_1_volumes}).
This means that when high-resolution imaging discovers a binary companion in 
a system that hosts a detected transiting planet, the planet is much
more likely to orbit the primary.
This statement is independent of the fact that planets are often confirmed to 
orbit the primary by inferring the stellar density from the transit duration.

\paragraph{On completeness}
{\bf TODO THIS SECTION}
This is if some fraction of stars you thought were searchable are not. There 
are no such stars.

Our expressions for the apparent rate density 
(Eqs.~\ref{eq:defn_apparent_rate_density} 
and~\ref{eq:model_1_apparent_rate_density}) do not explicitly mention 
detection efficiency.
If we were to take a smooth detection probability in S/N, we would need to 
include an explicit detection efficiency term in 
Eq.~\ref{eq:defn_apparent_rate_density} to inversely weight for planets 
that had low probabilities of being detected.
However, our ``detection probability'' is a step function in S/N 
(Eq.~\ref{eq:S_N_thresh}).
In our model, the maximum searchable distance is only a function of the 
apparent depth and true system luminosity.
Even though the observers are selecting stars based on what they think are 
``true radii'' (bottom row of Fig.~\ref{fig:model_1_volumes}), the 
actual searchability of a point-source is determined by apparent radius and 
system luminosity (Eq.~\ref{eq:S_N_thresh}; top rows of 
Fig.~\ref{fig:model_1_volumes}).
Thus at a given apparent radius $r\a$, the stars (single or binary) that are 
searchable are exactly the stars that are SEARCHED, since dilution affects the 
apparent radius and the maximum searchable distance in equal and opposite 
order.

@@

We then gave a general formula for the apparent rate density inferred by an 
observer ignoring binarity (Eq.~\ref{eq:general_Gamma_a}).
As input, this equations requires a volume-limited mass ratio distribution 
$f(q)$, and also the true rate densities for planets around singles, 
primaries, and secondaries.
The assumptions that make the model tractable are:
\begin{enumerate}
    \item the transit survey is S/N limited;
    \item all the primaries and single stars have identical properties;
    \item the properties of the secondaries can vary, but there are known 
    functions $L(M)$ and $R(M)$ that specify a star's luminosity and radius in 
    terms of its mass;
    \item the binarity-ignoring observers assume that binaries have the same 
    properties as the primaries.
\end{enumerate}

@@

All of these results should be understood as only being strictly applicable 
when the assumptions listed above are met.
Otherwise, they are only suggestive.
{\bf TODO: finish}

\acknowledgements{
It was a pleasure discussing this work with F. Dai and T. Barclay.

>>>>

\title{ The effects of binarity on planet occurrence rates measured by transit 
surveys}
%
\correspondingauthor{L. Bouma}
\email{luke@astro.princeton.edu}
%
\author{L. G. Bouma}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{K. Masuda}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{J. N. Winn}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
%
%
\begin{abstract}
%
This study develops simplified models of signal-to-noise limited transit 
surveys, in order to clarify the biases that stellar binarity introduces
to occurrence rate measurements.
Particular attention is paid to dilution of observed planet radii, errors in 
star counts, and treatment of detection efficiencies.
Given a somewhat restrictive set of assumptions, we derive a general formula 
for the apparent rate density, for which the free parameters include the true 
radius distribution of planets, and also the relative numbers of planets 
orbiting secondaries, primaries, and single stars.
From this formalism, we suggest that for most of the observed radius 
distribution (apparent planet radii $>2r_\oplus$), ignoring binarity only 
leads to errors in inferred occurrence rates at the $\lesssim 10\%$ level.
One corollary is that binarity seems unlikely to strongly influence the HJ 
rate discrepancy.
The errors created by ignoring binarity at smaller apparent radii might be 
larger: for instance, the absolute occurrence of Earth-sized planets could be 
overestimated by up to $\approx 50\%$.
A final point is that our formalism provides a quantitative argument for why
whenever high-resolution imaging follow-up discovers stellar neighbors of 
detected planets, the planet is more likely to orbit primary. 
%
\end{abstract}
%
\keywords{
    methods: data analysis ---
    planets and satellites: detection ---
    surveys}
%
%

@@

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        Inferred occurrence rates over $0.01r_\oplus$ bins in planet 
        radius, for a model with identical stars, identical planets, and twin 
        binaries.
        We assume a twin binary fraction of ${\rm BF}=0.1$, and that all 
        stars (single, primary, and secondary) host planets at equal 
        rates.
        If the true planet radius is $r\p$, all planets detected in binaries 
        will have apparent radii $r\a = r\p/\sqrt{2}$ (see 
        Eq.~\ref{eq:model_1_apparent_rate_density}).
        The rate and rate density are related by $\Lambda|_a^b = 
        \int_{a}^{b}\Gamma\,{\rm d}r$.
    }
    \label{fig:occ_rate_model_1}
\end{figure}

@@

To generalize the procedure of Sec.~\ref{sec:simplest}, we consider a SNR 
limited transit survey in which all the primaries and single stars have 
identical properties.
For example, they might all be solar analogs, roughly similar to 
the stars that {\it Kepler} surveyed~\citep{batalha_selection_2010}.
We let the properties of the secondaries vary, and assume that there are some 
functions $L(M)$ and $R(M)$ that specify a star's luminosity and radius in 
terms of its mass.
We then allow for an arbitrary volume-limited mass ratio distribution 
$f(q)$, and also for arbitrary true rate densities for singles, primaries, 
and doubles ($\Gamma_0, \Gamma_1, \Gamma_2$).
Since the properties of the secondaries vary, we must consider not only the 
dependence of the rate densities on planet radius, but also on stellar mass.
We presume that the observers always take the properties of a binary system to 
be those of the primary.

@@

\begin{figure}[!t]
    \centering
    \epsscale{1.15}
    \plottwo{figures/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf}
    \caption{
        {\it Left:} rate density and {\it right:} rate (over $0.5r_\oplus$ 
        bins) as a function of planet radius for the distribution specified by 
        Eq.~\ref{eq:model3_radius_distribution}. This model has identical 
        primaries and single stars, and varying secondaries. We use an 
        arbitrary normalization of $Z_0=0.5$ throughout.}
    \label{fig:occ_rate_model_3_log}
\end{figure}

@@

\paragraph{Fraction of detected planets from a given source}

\begin{figure}[!t]
    \centering
    \includegraphics[width=\textwidth]{figures/ndet_vs_radius_logx_model_3_fraclines_rpu_22.5_manyZs.pdf}
    \caption{
        Fraction of detected planet at a given apparent planet radius coming 
        from singles (solid lines), primaries (dashed lines), and secondaries 
        (dotted lines).
        Three different values for $Z_2/Z_0$ are selected: $1$ (blue), $0.5$ 
        (orange), $0$ (green).
        The assumed true planet radius distribution is a broken power-law
        (Eq.~\ref{eq:model3_radius_distribution}; same as 
        Fig.~\ref{fig:occ_rate_model_3_log}).
    }
    \label{fig:frac_model_3}
\end{figure}

It would be nice to get some intuition for how much the secondaries matter.
From Fig.~\ref{fig:model_1_volumes}, we have the intuition that for a given 
true planet radius, secondaries have a much smaller searchable volume than 
primaries or singles.
Does this necessarily imply that if we are given a detected planet with some 
apparent radius $r\a$, which is then observed by high-resolution imaging to 
exist in a binary, that the planet probably orbits the primary?

We explore this quantitatively in Fig.~\ref{fig:frac_model_3}.
The lines in this figure are computed using the expressions given in the 
appendix for the number of detections coming from singles, primaries, and 
secondaries (Eqs.~\ref{eq:n_det_0},~\ref{eq:n_det_1}, and~\ref{eq:n_det_2}).
In the scenario that high-resolution imaging finds a system with $r\a > 
2r_\oplus$ in a binary, of order $\sim 3\times$ more detected planets orbit 
primaries than secondaries, for the $Z_2/Z_0=1$ case.
For the $Z_2/Z_0=0.5$ case, of order $\sim 7\times$ more detected planet 
planets orbit primaries than secondaries.
At $r\a < 2r_\oplus$, the ratios are $\sim 1.6 \times$ and $\sim 3.1 \times$ 
as many detected planets orbiting primaries than secondaries for the same 
$Z_2/Z_0$ values.

@@

@@

\begin{figure}[!t]
    \centering
    \epsscale{1.15}
    \plottwo{figures/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf}
    \caption{
        {\it Left:} rate density and {\it right:} rate (over $0.25r_\oplus$ 
        bins) as a function of planet radius in a model with a radius gap 
        (Eq.~\ref{eq:model4_radius_distribution}).
        Similar to Fig.~\protect\ref{fig:occ_rate_model_3_log}, this model has 
        fixed primaries and single stars, but varying secondaries.
    }
    \label{fig:model_4}
\end{figure}

@@

\paragraph{How has binarity been considered in occurrence rate measurements?}
This study has shown that under a reasonable set of simplifying assumptions, 
ignoring binarity introduces systematic errors to star and planet counts in 
transit surveys, which then bias derived occurrence rates.
Thus far, real-world occurrence rate calculations\footnote{
    A list of occurrence rate papers is maintained at 
    \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
} using transit survey data have mostly ignored stellar 
multiplicity~\citep[\textit{e.g.},][]{howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,dressing_occurrence_2015,burke_terrestrial_2015}.
For {\it Kepler} occurrence rates specifically, 
it seems that no one has yet carefully assessed binarity's importance, or lack 
thereof.
While we do not resolve the problem, we do suggest the approximate scale of 
the possible errors in a survey-independent manner.

Of course, on a system-by-system level stellar multiplicity affects the 
interpretation of planet candidates. High resolution imaging 
campaigns have measured the multiplicities of almost all {\it Kepler}\ Objects 
of Interest 
\citep{howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
    horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
    law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
    wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016,ziegler_robo-ao_2017}.
The results of these programs have been collected 
by~\citet{furlan_kepler_2017}, and they represent an important advance in 
understanding the KOI 
sample's multiplicity statistics.
In particular, they can be immediately applied to rectify binarity's effects 
on the mass-radius diagram~\citep{furlan_densities_2017}.

This high resolution imaging campaign is also beginning to connect with
occurrence rate calculations.
The most recent rate studies have used~\citet{furlan_kepler_2017}'s 
catalog to test the effects of removing KOI hosts with known companions, which 
helps reduce contamination in the ``numerator'' of 
the occurrence rate (\citealt{fulton_california-_2017}; 
\citealt{petigura_CKS_2017}).
However, without an understanding of the multiplicity statistics of the 
non-KOI stars, the true number of searchable stars, and thus the true 
occurrence rates, will remain biased.

\paragraph{Practical effects: smooth detection efficiencies; finite SNR floors}
To interpret whether the results of this study are of any help for removing 
binarity's effects from the {\it Kepler}\ planet sample, a few practical 
concerns become pressing.

First, our calculations have ignored the fact that any given transit survey's 
finite SNR floor might censor the apparent rate density.
If the surveyed stars all have the same size, this is equivalent to 
saying that there might be a cutoff in apparent planet radii, below which no 
planets are detected.
The effects on our main results (e.g., 
Figs.~\ref{fig:occ_rate_model_3_log},~\ref{fig:frac_model_3}, 
and~\ref{fig:gaussian_HJ}) would be that the apparent rate density 
below the cutoff in apparent radius would simply drop to zero.

A second assumption we used is that the detection efficiency is a 
step function in SNR.
The detection efficiencies of real transit surveys are smooth functions in 
SNR; see for example the injection \& recovery simulations performed on {\it 
    Kepler}\ data by~\citet{christiansen_measuring_2016}, and the resulting 
smooth 
functional form adopted by~\citet{fulton_california-_2017}.
If we were to take a smooth detection probability in SNR, we would need to 
include a detection efficiency term in 
Eq.~\ref{eq:defn_apparent_rate_density} to inversely weight for planets 
that had low probabilities of being detected.

The simplest way to avoid the conceptual complications of accounting for 
finite detection efficiency is to raise the SNR floor, to {\it e.g.,} 
${\rm SNR} \approx 12$ in \citet{fulton_california-_2017}'s Fig 5.
To a good approximation, this allows one to discuss stars that are 
``searchable'' and ``not searchable'' for signals of an observed depth (at 
fixed orbital period).
For {\it Kepler} specifically, coupled with high resolution imaging of a
comparison sample of non-KOI host stars, this would facilitate the process 
of directly comparing the observed KOI distribution of apparent radii with the 
distributions discussed in this study.

If one insists on using a smooth detection efficiency, then life probably 
becomes more complicated.
It might then be necessary to model the detection pipeline's efficiency while 
somehow marginalizing over binarity.
Since the relative number of detections (at fixed $\delta_{\rm obs}$) coming 
from singles, primaries, and secondaries changes as a function of the 
intrinsic distribution of planet parameters (Fig.~\ref{fig:frac_model_3}), 
some complicated deconvolution might be required.

\paragraph{The rate of Earth analogs}
Per {\it Kepler}'s primary science objective, the rate of Earth-like planets 
orbiting Sun-like stars has been independently measured by 
\citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
    foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
These efforts have found that the one-year terrestrial planet occurrence rate 
varies between $\approx 0.03$ and $\approx 1$ per Sun-like star, depending on 
assumptions that are made when retrieving the rate 
(\citealt{burke_terrestrial_2015}'s Fig.~17).
In the power law model of Sec.~\ref{sec:model_3}, we noted that the inferred 
rate can be up to 50\% higher than the true rate around single stars.
Though this bias seems large, it is currently small compared to the other 
systematic factors that dominate the dispersion in $\eta_\oplus$ 
measurements.
If a future analyses determine absolute values of $\eta_\oplus$ to 
better than a factor of two, binarity might merit closer attention.

One relevant caveat to our assessment of binarity's importance for 
$\eta_\oplus$ measurements is that none of our models 
included the rate density's period-dependence. However, close binaries usually
provoke dynamical instabilities, leading to fewer long-period planets per 
star~\citep[\textit{e.g.},][]{holman_long-term_1999,wang_influence_2014,
    kraus_impact_2016}.
This effect might further affect transit survey measurements of $\eta_\oplus$
beyond our rough estimate.

\paragraph{The hot Jupiter rate discrepancy}
There is at least one context in which ignoring binarity has been suggested as 
a possible source of discrepant occurrence rate measurements.
Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
marginally lower than those found by radial velocity surveys ($\approx 1\%$; 
see Table~\ref{tab:hj_rates}).
Though the discrepancy has weak statistical significance ($<3\sigma$),
one reason to expect a difference is that the corresponding stellar 
populations have distinct metallicities.
As argued by \citet{gould_frequency_2006}, the RV sample is biased towards 
metal-rich stars, which have been measured by RV surveys to preferentially 
host more giant 
planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005}.
Investigating the discrepancy from the metallicty 
angle,~\citet{guo_metallicity_2017} measured the
{\it Kepler} field's mean metallicity to be $[{\rm M/H}]_{\rm Kepler}= 
-0.045\pm0.009$, which is lower than the California Planet Search's mean of 
$[{\rm M/H}]_{\rm CPS}= -0.005\pm0.006$.
The former value agrees with that measured by \citet{dong_metallicities_2014}.
Refitting for the metallicity exponent in $\Lambda_{\rm HJ} \propto 10^{\beta 
[{\rm M/H}] }$, \citeauthor{guo_metallicity_2017}\! found $\beta = 2.1\pm 
0.7$, and noted that this would imply that the metallicity difference could 
account for a $\approx 20\%$ relative difference in the measured rates between 
the CKS and {\it Kepler}\ samples~--~not a factor of two\footnote{
\citet{petigura_CKS_2017} recently found $\beta = 3.4^{0.9}_{-0.8}$.
This gives an $\approx 25\%$ relative difference, indicating metallicity could 
account for about half of the ``hot Jupiter rate discrepancy''.
}.
\citeauthor{guo_metallicity_2017}\! concluded that ``other factors, such as 
binary contamination and imperfect stellar properties'' must also be at play.

@@

\paragraph{Does a detected planet orbit the primary or secondary?}
\citet{ciardi_understanding_2015} studied the effects of stellar multiplicity 
on the planet radii derived from transit surveys.
They modeled the problem for {\it Kepler}\ objects of interest by matching a 
population of binary and tertiary companions to KOI stars, 
under the assumption that the KIC-listed stars were the primaries.
They then computed planet radius correction factors assuming that {\it 
    Kepler}-detected planets orbited the primary or companion stars
with equal probability (their Sec.~5).
Under these assumptions, they found that any given planet's radius is on 
average underestimated by a multiplicative factor of $\approx\! 1.5$.
\citet{ziegler_robo-ao_2017} recently reported a similar mean radius 
correction factor for the multiple systems observed by the Robo-AO KOI survey, 
using the same assumption that detected planets are as likely to orbit the 
primary and the secondary.

Assuming a broken power-law radius distribution, we showed in 
Fig.~\ref{fig:frac_model_3} that assuming a detected planet has equal 
probability of orbiting the primary or secondary leads to an overestimate of
binarity's population-level effects.
A planet orbiting the secondary does lead to extreme corrections.
However, at $r\a \gtrsim 2r_\oplus$, these cases are rare outliers.
At $r\a \lesssim 2r_\oplus$, for all of the trial values of $Z_2/Z_0$ assumed 
in Fig.~\ref{fig:frac_model_3}, a detected planet is always more likely to 
orbit the primary than the secondary.

Of course, our model's assumptions (see the list in Sec.~\ref{sec:conclusion}) 
might not apply to the {\it Kepler}\ dataset.
If they do, then for the $56\%$ of ``\texttt{CONFIRMED}'' 
KOIs\footnote{Exoplanet Archive; \cite{akeson_nasa_2013}; 
\url{exoplanetarchive.ipac.caltech.edu}} with 
apparent radii $>2r_\oplus$, 
whenever high-resolution imaging 
discovers a binary companion in 
a system that hosts a detected transiting planet, the planet is much
more likely to orbit the primary.
This statement is independent of the fact that planets are often confirmed to 
orbit the primary by inferring the stellar density from the transit duration.

@@

We then gave a general formula for the apparent rate density inferred by an 
observer ignoring binarity (Eq.~\ref{eq:general_Gamma_a}).
As input, this equation requires a volume-limited mass ratio distribution 
$f(q)$, and also the true rate densities for planets around singles, 
primaries, and secondaries.
The assumptions that make the model tractable are:
\begin{enumerate}
    \item the transit survey is SNR limited;
    \item all the primaries and single stars have identical properties;
    \item the properties of the secondaries can vary, but there are known 
    functions $L(M)$ and $R(M)$ that specify a star's luminosity and radius in 
    terms of its mass;
    \item the binarity-ignoring observers assume that binaries have the same 
    properties as the primaries.
\end{enumerate}

@@

All of these results should be understood as only being strictly applicable 
when the assumptions listed above are met.
Otherwise, while it is only suggestive, our approach still provides 
helpful hints at how stellar binarity influences transit survey occurrence 
rates.

\acknowledgements{
It was a pleasure sharing discussions about this study with F. Dai and T. 
Barclay.
This work made use of NASA's Astrophysics Data System Bibliographic Services.
